\documentclass{article}
\usepackage{scimisc-cv}
\usepackage{hyperref}
\hypersetup{pdfborder = {0 0 0}}

\title{Shreesha's Resume}
\author{Shreesha Krishna Rao}
\date{Mar 2026}

%% These are custom commands defined in scimisc-cv.sty

\cvname{Shreesha Krishna Rao}

\cvpersonalinfo{

+ 91 8762484704 \cvinfosep
\href{shreeshasrk33@gmail.com}{raoshreeshakrishna@gmail.com}
\cvinfosep
\href{https://www.linkedin.com/in/shreesha-krishna-rao-50438223a/}{LinkedIn}
 \cvinfosep
\href{https://github.com/Shreesha-K-Rao}{GitHub}
 \cvinfosep
}



\begin{document}

% \maketitle %% This is LaTeX's default title constructed from \title,\author,\date

\makecvtitle %% This is a custom command constructing the CV title from \cvname, \cvpersonalinfo

\section{SUMMARY}
Results-driven software engineer with 4 years of experience in network automation and data analytics in networking domain. Proficient in network automation techniques that include IT service management, workflow orchestration, cloud infrastructure management, and continuous integration and deployment. Well-versed in data analysis, business intelligence, reporting, and predictive modeling. Skilled at using automated approaches to streamline network operations and improve performance. Proven ability to collaborate across teams and achieve effective, high-impact results.





\section{EDUCATION}
% \cvsubsection{College Of Business}[University Of Texas At Arlington, Arlington, TX]
% [Master of Science in Business Analytics][\normalfont August  2023 - Dec 2024]

\cvsubsection{Visvesvaraya Technological University}[Sep 2018 - Jul 2022]
[Bachelors in Information Science  and Engineering][\normalfont Bengaluru, India] 

 
\section{Skills}

\begin{itemize}
\item[] \textbf{Languages:} Python, SQL, C++
\item[] \textbf{DevOps:} Apache Airflow, Ansible, Grok, LogicMonitor, ServiceNow
\item[] \textbf{Database: } MSSQL
\item[] \textbf{Visualization: } Power BI
\item[] \textbf{Other tools: } Microsoft Office Suite, Cloud, Qlik, Postman, JIRA

\end{itemize}


\section{WORK EXPERIENCE}


\cvsubsection{Software Engineer, Research and Development}[Bengaluru, KA, IND]
[NTT DATA INC.][\normalfont Aug 2023 - Present]
\begin{itemize}
\item Automated inventory discovery workflows for controller and non-controller pre-sales based environments with CMDB integration thereby, reducing manual efforts by 70\% and improved inventory accuracy by 45\% , enhancing asset viability
\item Implemented an automated device bandwidth utilization workflow integrating validation, execution and ticketing. Reduced manual triage by 60\% and improved operational efficiency
\item Extended configuration backup automation to support multi-vendor environments, onboarding various technologies and implementing standard worflow orchestration, validation and backup execution, increasing technology coverage by 20\%, reducing manual efforts by 65\% thereby improving backup consistency and SLA adherence 
\item Automated vendor notification security advisory workflow and EOX/EOL workflow using Apache Airflow and Python, streamlining ingestion, validation,prioritization and alert routing, reduced manual effort by 78\% and improved notification turnaround time by 64\%, accelerating security response efficiency
\item Designed and implemented solutions with a focus on optimizing business processes and supporting informed decision-making through data insights
\item  Built a CI/CD pipeline using Azure DevOps and Azure Functions to monitor network device status, increasing efficiency and reliability by 35\%.
\item  Automated ServiceNow procedures to streamline logging, resulting in a 30\% cost savings in development.
\item  Deployed Azure Data Factory ETL pipelines to improve network configurations, resulting in a 70\% boost in productivity.

\item  Developed and implemented strategies to streamline company quality, such as automation utilizing Power Automate, resulting in a 20\% increase in operational efficiency.

\item  Created meaningful operational dashboards and reports using Power BI that addressed business, process, and system concerns, promoting informed decision-making and generating a 25\% boost in process optimization. Additionally, streamlined corporate operations which resulted in increase in valuable insights.

\item  Gathered and grasped business requirements from stakeholders for data visualization and analysis, improving Power BI performance and reducing data refresh times by 15\%.

\item  Collaborated with data engineers and analysts to collect, clean, transform, and model data for reporting, resulting in a 45\% increase in data quality.

\end{itemize}


\cvsubsection {Graduate Trainee}[Bengaluru, KA, IND]
[NTT Ltd. ] [\normalfont Aug 2022 - Jul 2023]
\begin{itemize}
\item Gained a solid foundation in advanced networking topics such as Network Security, Firewalls, and Routing Protocols, which are essential for managing corporate networks.
\item Developed expertise in Network Automation, enabling simpler methods for managing and monitoring network operations, resulting in a 30\% boost in operational efficiency.
\item Built data processing pipelines with Microsoft Azure Data Factory, automating 85\% of data activities and streamlined data analysis by linking MySQL data to Power BI, decreasing manual involvement by 40\% and increasing decision-making speed.
\item Collaborated with vendors such as Cisco, Palo Alto and VMware to improve server query response times via APIs, resulting in a 20\% increase in query speed. Additionally, contributed to reducing human intervention in server management through the use of APIs and automation technologies, cutting manual operations by 50\%.
\end{itemize}
\end{document}